```{r}
library(tidyverse)
```

b. Find the correlation between age and circumference of Orange dataset. Show the relation 
graphically.(   QUESTION    )
```{r}
Orange
cor.test(Orange$age,Orange$circumference)
g=Orange %>% ggplot(aes(x=age,y=circumference))
g+geom_line(color="red")+geom_smooth()
g+geom_point()
```
b. Find the correlation between age and circumference of Orange dataset. Show the relation 
graphically.(   QUESTION    )

```{r}
#factor color depends on the data 
#qplot(age,data=Orange,geom='histogram',color=factor(cyl))+labs(x="xaxis",y="ccc")
qplot(displ,data=mpg,geom='histogram',color=factor(cyl))+labs(x="fbbfd")

```


```{r}

```


```{r}
p1=data.frame(u=c("uzair","qq","aa"),
              w=c(1,2,3),
              e=c(122,33,44),
              row.names = c('q','s','dd'),stringsAsFactors =FALSE)
# if u miss one attribute also in the colnames u will still get the coutput
colnames(p1)=c("1st","","3rd")
p1
```
1. Build the suitable model to find the relation between the marks of a student and number of 
hours studied. Also show graphically. Predict the marks of a student with 6 hours studied. 
Hours Marks
3 65
3.5 67
2 58
4 72
4.5 78
5 83
6.3 85
7 89

```{r}
df = data.frame(
  Hou = c(3, 3.5, 2, 4, 4.5, 5, 6.3, 7),
  Marks = c(65, 67, 58, 72, 78, 83, 85, 89)
)
Hou = c(3, 3.5, 2, 4, 4.5, 5, 6.3, 7)
  Marks = c(65, 67, 58, 72, 78, 83, 85, 89)
rel=lm(Marks~Hou)
print(summary(rel))

```


```{r}
d1=data.frame(Hou=6)
pp=predict(rel,d1)
print(pp)
```
q2)2 . Build a suitable model to find the relation between the variables sepal length, petal length of 
iris dataset. Explain the summary of the model. Predict the petal length for sepal length of 3.2


```{r}

iris
re=lm(iris$Petal.Length~iris$Sepal.Length)
summary(re)
rr=data.frame(Sepal.Length=3.2)
pre=predict(re,rr)
print(pre)
```
3. a. Test whether two proportions 43 out of 120 and 56 out of 110 are statistically same or 
different


```{r}
prop.test(c(43,56),c(120,110))
```
b. Find the correlation between age and circumference of Orange dataset. Show the relation 
graphically.


```{r}
cor.test(Orange$age,Orange$circumference)
g=Orange %>% ggplot(aes(x=age,y=circumference))
g+geom_line(color='purple')
```
c. Find the relation between gears and am variables of mtcars dataset. Explain the hypothesis 
and conclusion

```{r}
mtcars
d=table(mtcars$gear,mtcars$am)
d
chisq.test(d)
fisher.test(d)
```
4. a. Find the correlation between passengers in the months Jan and Feb of AirPassengers 
dataset. Show the relation graphically.


```{r}
AirPassengers
jan=c(112,115,145,171,196,204,242,284,315,340,360,417)
feb=c(118,126,150,180,196,188,233,277,301,318,342,391)
cor.test(jan,feb)
```

b. Analyze the variance between Airbags, type and price of Cars93 dataset. Explain the hypothesis 
and conclusion

```{r}
Cars93
a=aov(Price~Type*AirBags,data=Cars93)
a
```
c. Find out is there any significant correlation between the types of car sold and the type of Air 
bags it has from Cars93 dataset
# ye WALA CORRELATION NAHI THA THIS IS CHISQ BUT QUESTION SAYS (significant CORRELATION WTF)
```{r}
Cars93
#cr=data.frame(type=c(Cars93$Type),air=c(Cars93$AirBags))
cr=table(Cars93$Type,Cars93$AirBags)
cr
chisq.test(cr)

```
5. Predict the salary of a person with the years of experience 3.5. Plot the graph that shows the 
relation between years experienced and Salary using ggplot2.
Years experienced Salary
 1.1 393
 1.3 462
 1.5 377
 2.0 435
 2.2 398
 2.9 566
 3.0 601
 3.2 544
 3.7 571


```{r}
dff <- data.frame(
  Years = c(1.1, 1.3, 1.5, 2.0, 2.2, 2.9, 3.0, 3.2, 3.7),
  Salary = c(393, 462, 377, 435, 398, 566, 601, 544, 571))
  Years = c(1.1, 1.3, 1.5, 2.0, 2.2, 2.9, 3.0, 3.2, 3.7)
  Salary = c(393, 462, 377, 435, 398, 566, 601, 544, 571)

re=lm(Salary~Years)
summary(re)
red=data.frame(Years=3.5)
pr=predict(re,red)
print(pr)

```
6. Write a R program to find the relation between the independent variables disp, wt and 
dependent variable vs. Find the accuracy of the model

```{r}
mtcars
q=aov(vs~factor(disp+wt),data=mtcars)
q

```
7. a. Find the correlation between sepal length and petal length of iris dataset. Show the relation 
graphically.


```{r}
cor.test(iris$Sepal.Length,iris$Petal.Length)
qplot(Sepal.Length,Petal.Length,data=iris,geom=c("line","smooth"))
```
b. Test whether two proportions 23 out of 90 and 34 out of 110 are statistically same or different


```{r}
prop.test(c(23,34),c(90,110))
```

c. Find the mean variance between Airbags, type and price of Cars93 dataset

```{r}
a=aov(Price~Type*AirBags,data=Cars93)
a
```
#8. a. Find correlation between wind and temp of airquality dataset and plot a scatterplot using ggplot2

```{r}
airquality
cor.test(airquality$Temp,airquality$Temp)
ggplot(data=airquality)+geom_line(mapping =aes(x=Wind,y=Temp))
```
#b. Find the relation between manufacturer and type variables Cars93 dataset


```{r}
b=table(Cars93$Manufacturer,Cars93$Type)
chisq.test(b)

```
#c. Find the mean variance between gears and hp variables of mtcars dataset

```{r}
mtcars
mea=aov(gear~hp,data=mtcars)
mea
```
9. A multiplex INOX charges the following rates for the parking as given below. Write R program 
which will take hours as an input and calculate parking bill according to the given table. 
 Hours Rate of charge 
 < 1 Rs .40 
 1-2 Rs 60 
 2-3 Rs 80 
 Above 3 Rs 100

```{r}
n=as.integer(readline("enter the number"))

if(n>=1)
{
  print("rupeees 40")
}else if(n>=1 && n<=2)
  {
    print("rupees 60")
}else if(n>=2 && n<=3)
{
  print("rupees 80")
}else if(n>3){
  print("100 ruppees")
}else{
  print("fucked")
}


```

# Write R program to check whether a number is prime or not. 
```{r}

primen=function(n)
{
  count=0
  if(n<=1)
  {
    return(FALSE)
  }
  else if(n==2)
  {
    return(TRUE)
  }
  for(i in 1:n)
  {
    if(n%%i==0){
      count=count+1
    }
  }
  if(count==2)
  {
    print("the number is prime")
  }
  else{
    print("the number is not prime")
  }
}
n=as.integer(readline("enter the number to check weather the number is prime or not"))
primen(n)
```
11. Write R program for the following questions 

a) Create a data frame Employee with the variables name, age, dept and salary with four rows. 



```{r}
# Create the data frame
em <- data.frame(
  name = c("John", "Sarah", "Michael", "Emily"),
  age = c(32, 28, 35, 30),
  dept = c("HR", "Marketing", "Finance", "IT"),
  salary = c(50000, 60000, 70000, 55000)
)

# Print the data frame
print(em)

library(dplyr)
```
b) Add new column address and display the columns, name and address

```{r}
em$address=c("cannada","mumbai","america","london")
select(em,name,address)
em
```
c) Sort the employee name based on salary in ascending order and display the employee with 
maximum salary.

```{r}
library(dplyr)

# Sort the data frame by salary in ascending order and display employee with maximum salary
Employee %>%
  arrange(salary) %>%
  filter(row_number() == n()) 

```

```{r}
q=em %>% arrange(salary) %>% select(name,salary)
q
q[4,]
```

d) Remove the column address and display 2nd and 3rd row with name and age of the employee.

```{r}
#em=select(em,-address)
em[c(2:3),c(1,2)]
```

e) Find the employee whose age is between 35 and 40

```{r}
filter(em,age==35 & age <=40) %>% select(name)
```
f) Update salary of all employees by 5000. Plot bar graph to show the updated salaries

```{r}
#mutate(em,salary=salary+5000)
barplot(em$salary, names.arg = em$name, xlab = "Employee", ylab = "Salary", main = "Updated Salaries")
```
13. Write R program for the following questions 
a) Create a data frame Product with the variables name, price, rating and quantity with four 
rows. 


```{r}
# Create the data frame
p11 <- data.frame(
  name = c("Product A", "Product B", "Product C", "Product D"),
  price = c(10.99, 19.99, 15.50, 12.75),
  rating = c(4.5, 3.8, 4.2, 4.0),
  quantity = c(100, 50, 75, 120)
)

# Print the data frame
print(P11)

```

b) Add the column shop_name and display the data frame with product name and shop_name.

```{r}
p11=cbind(p11,shp_nm=c("kasim","bakala","mbakala","othaim"))
p11
```
c) Sort the product name based on price in descending order and display the product with 
maximum price.


```{r}
q1=p11 %>% arrange(desc(price)) 
q1
```

d) Remove the column, rating and display 1st and 3rd row with name and rating of the product.

```{r}
p11=select(p11,-rating)
p11[c(1:3),]
```
e) Find the product whose rating is between 5 and 10


```{r}
filter(p11,rating >2 & rating<=10)
```
f) Increment the price of all products by 15 Rs. Plot bar graph to show the updated price with 
product name.

```{r}
#p11=mutate(p11,price=price+15)

barplot(p11$price,names.arg = p11$name,col="green")
```

# THE OTHER DATA FRAME PRACTISE QUESTIONS
```{r}
st=data.frame(name=c('A','B','C'),
 rollno=c(101,102,103),
 age=c(21,24,23),
 marks=c(50,43,56))

st
```


```{r}
str(st)
summary(st)
```



```{r}
st[,1]
st[c(1:2),]
st[c(3:4),c(1:3)]

```


```{r}
st=cbind(st,address=c("usa","ksa","canada"))
st
```


```{r}
st=select(st,-address)
st
```


```{r}
st=st[-c(2,3),]
st
```


```{r}
arrange(st,name)
```


```{r}

```

